---
title: "5207 assignment"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
date: "2023-11-11"
editor_options:
  markdown:
    wrap: 72
---
```{r setup}
options(repos = c(CRAN = "https://cloud.r-project.org/"))
```

1.  install packages

```{r}
library(dplyr)
library(summarytools)
library(ggplot2)
```

read data set

```{r}
data <- read.csv("C:/Users/Administrator/Desktop/5207/Rateprof.csv")
```

3.  descriptive statistics

```{r}
summary(data)
str(data)

barplot_vars <- c("gender", "discipline", "dept","pepper") 
               for (var in barplot_vars) {
                    p <- ggplot(data, aes(x = !!sym(var))) +
                         geom_bar() +
                         ggtitle(paste("Bar Plot of", var)) 
                    print(p)
}

histogram_vars <- c("numYears", "numRaters", "numCourses","quality",
                    "helpfulness","clarity", "easiness", "raterInterest",
                    "sdQuality","sdHelpfulness", "sdClarity", "sdEasiness", 
                    "sdRaterInterest")
                for (var in histogram_vars) { 
                     p <- ggplot(data, aes(x = !!rlang::sym(var))) + 
                          geom_histogram(binwidth = 1) +
                          ggtitle(paste("Histogram of", var)) 
                     print(p) 
}
```

Data analysis process

Q1:How are the five ratings related? Describe

```{r}
matrix <- cor(data[, c("quality","helpfulness", "clarity", "easiness", 
                       "raterInterest")]) 
print(matrix)
```

perform heat map to virtualize correlations

```{r}
install.packages("pheatmap")
library(pheatmap)
pheatmap(matrix)
```

Build Linear Regression Model and check 4 basic assumption According to
the plot below, LM meets all assupmtions, including linearity,
independence of residuals, normality of residuals and homoscedasticity.
For linearity,

```{r}
pairs(data[, c("quality", "helpfulness", "clarity", "easiness", "raterInterest")]) 
data$gender <- as.factor(data$gender) 
data$discipline <- as.factor(data$discipline) 
data$pepper <- as.factor(data$pepper)
model <- lm(quality ~ gender + numYears + discipline + easiness + 
                      raterInterest + pepper,
            data = data) 
summary(model) 
par(mfrow = c(2, 2)) 
plot(model)

plot(fitted(model), sqrt(abs(residuals(model))))
abline(h = 0, col = "red")
```

ANOVA to check the effects of predictors

```{r}
anova(model)
```
